EuPPollNet: A European database of plant-pollinator networks

### 2024-09-05 Manuscript/EuPPollNet_Ms.qmd
check why this curve doesn't match now

#Increase doubling effort
##Pollinators
poll_increase = poll_output$iNextEst$Network_id
poll_increase1 = poll_increase %>% filter(method == "observed") %>% pull(qD)
poll_increase2 = poll_increase %>% filter(t == max(t)) %>% pull(qD)
poll_increase3 = (poll_increase2-poll_increase1)/poll_increase1 * 100
##Plants
plant_increase = plant_output$iNextEst$Network_id
plant_increase1 = plant_increase %>% filter(method == "observed") %>% pull(qD)
plant_increase2 = plant_increase %>% filter(t == max(t)) %>% pull(qD)
plant_increase3 = (plant_increase2-plant_increase1)/plant_increase1 * 100
##Interactions
int_increase = int_output$iNextEst$Network_id
int_increase1 = int_increase %>% filter(method == "observed") %>% pull(qD)
int_increase2 = int_increase %>% filter(t == max(t)) %>% pull(qD)
int_increase3 = (int_increase2-int_increase1)/int_increase1 * 100
##Pollinator by plant
plant_poll_increase = plant_poll_output$iNextEst$Plant_id
plant_poll_increase1 = plant_poll_increase %>% filter(method == "observed") %>% pull(qD)
plant_poll_increase2 = plant_poll_increase %>% filter(t == max(t)) %>% pull(qD)
plant_poll_increase3 = (plant_poll_increase2-plant_poll_increase1)/plant_poll_increase1 * 100

@@

#Pollinators-----
poll_output = readRDS("../Data/Working_files/pollinator_sampling_coverage.rds")
pollinators_curves = readRDS("../Data/Working_files/collectors_curves_pollinators.rds")
#Create dataset
d_poll = poll_output$iNextEst$Network_id
#Check cols
d_poll$col = d_poll$method

#Now create tibble with same structure
a_poll = tibble(t = pollinators_curves$Study_sampled, 
           method = as.character(pollinators_curves$iteration), 
           qD = pollinators_curves$Unique_spp_cumulative,
           col = "collectors")

#Bind datasets 
d_poll1 = bind_rows(d_poll, a_poll)
d_poll1_point = d_poll1 %>%  filter(method == "observed")
d_poll1_lines = d_poll1 %>%  filter(!method == "observed")

#Order levels
d_poll1_lines$col = factor(d_poll1_lines$col, levels = c("collectors", "interpolated", "extrapolated"))
#Plot
p1 = ggplot(d_poll1_lines, aes(x = t, y = qD, group = method, color = col)) +
geom_line(aes(linetype = col),size = 0.65) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_poll1_point, col = "black", size=2) + 
ylab("Pollinator species") +
xlab("Networks") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off")  +
xlim(0,3000)+
ylim(0, 3000) +
ggtitle("(a)") +
theme(plot.margin = margin(r = 12))

#Plants-----
plant_output = readRDS("../Data/Working_files/plant_sampling_coverage.rds")
plant_curves = readRDS("../Data/Working_files/collectors_curves_plants.rds")
#Create dataset
d_plant = plant_output$iNextEst$Network_id
#Check cols
d_plant$col = d_plant$method

#Now create tibble with same structure
a_plant = tibble(t = plant_curves$Study_sampled, 
           method = as.character(plant_curves$iteration), 
           qD = plant_curves$Unique_spp_cumulative,
           col = "collectors")

#Bind datasets 
d_plant1 = bind_rows(d_plant, a_plant)
d_plant1_point = d_plant1 %>%  filter(method == "observed")
d_plant1_lines = d_plant1 %>%  filter(!method == "observed")

#Order levels
d_plant1_lines$col = factor(d_plant1_lines$col, levels = c("collectors", "interpolated", "extrapolated"))
#Plot
p2 = ggplot(d_plant1_lines, aes(x = t, y = qD, group = method, color = col)) +
geom_line(aes(linetype = col), size = 0.65) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_plant1_point, col = "black", size=2) + 
ylab("Plant species") +
xlab("Networks") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off")  +
xlim(0,3000)+
ylim(0, 3000)+
ggtitle("(b)")+
theme(plot.margin = margin(r = 12))

#Interactions-----
int_output = readRDS("../Data/Working_files/interactions_sampling_coverage.rds")
interactions_curves = readRDS("../Data/Working_files/collectors_curves_interactions.rds")
#Create dataset
d_int = int_output$iNextEst$Network_id
#Check cols
d_int$col = d_int$method

#Now create tibble with same structure
a_poll = tibble(t = interactions_curves$Study_sampled, 
           method = as.character(interactions_curves$iteration), 
           qD = interactions_curves$Unique_spp_cumulative,
           col = "collectors")

#Bind datasets 
d_int1 = bind_rows(d_int, a_poll)
d_int1_point = d_int1 %>%  filter(method == "observed")
d_int1_lines = d_int1 %>%  filter(!method == "observed")

#Plot
#Order levels
d_int1_lines$col = factor(d_int1_lines$col, levels = c("collectors", "interpolated", "extrapolated"))
#Plot
p3 = ggplot(d_int1_lines, aes(x = t, y = qD, group = method, color = col)) +
geom_line(aes(linetype = col), size = 0.65) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_int1_point, col = "black", size=2) + 
ylab("Unique interactions") +
xlab("Networks") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off")  +
xlim(0,3000) +
ylim(0, 30000)+
ggtitle("(c)")

@@

#Create dataset
d_pp = plant_poll_output$iNextEst$Plant_id
#Check cols
d_pp$col = d_pp$method

#Now create tibble with same structure
a_poll = tibble(t = plant_poll_curves$Plant_sampled, 
           method = as.character(plant_poll_curves$iteration), 
           qD = plant_poll_curves$Unique_spp_cumulative,
           col = "collectors")

#Bind datasets 
d_pp1 = bind_rows(d_pp, a_poll)
d_pp1_point = d_pp1 %>%  filter(method == "observed")
d_pp1_lines = d_pp1 %>%  filter(!method == "observed")

#Plot
#Order levels
d_pp1_lines$col = factor(d_pp1_lines$col, levels = c("collectors", "interpolated", "extrapolated"))
#Plot
pp1 = ggplot(d_pp1_lines, aes(x = t, y = qD, group = method, color = col)) +
geom_line(aes(linetype = col)) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_pp1_point, col = "black") + 
ylab("Pollinator species") +
xlab("Plant species") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off") +
ggtitle("(d)") +
scale_x_continuous(breaks = seq(0, 2800, by = 1000), limits=c(0,2800)) +
scale_y_continuous(breaks = seq(0, 2600, by = 1000), limits=c(0,2600)) +
theme(legend.position = "none")

>>>>

#Increase doubling effort
##Pollinators
poll_increase = poll_output$iNextEst$coverage_based
poll_increase1 = poll_increase %>% filter(Method == "Observed") %>% pull(qD)
poll_increase2 = poll_increase %>% filter(t == max(t)) %>% pull(qD)
poll_increase3 = (poll_increase2-poll_increase1)/poll_increase1 * 100
##Plants
plant_increase = plant_output$iNextEst$coverage_based
plant_increase1 = plant_increase %>% filter(Method == "Observed") %>% pull(qD)
plant_increase2 = plant_increase %>% filter(t == max(t)) %>% pull(qD)
plant_increase3 = (plant_increase2-plant_increase1)/plant_increase1 * 100
##Interactions
int_increase = int_output$iNextEst$coverage_based
int_increase1 = int_increase %>% filter(Method == "Observed") %>% pull(qD)
int_increase2 = int_increase %>% filter(t == max(t)) %>% pull(qD)
int_increase3 = (int_increase2-int_increase1)/int_increase1 * 100
##Pollinator by plant
plant_poll_increase = plant_poll_output$iNextEst$coverage_based
plant_poll_increase1 = plant_poll_increase %>% filter(Method == "Observed") %>% pull(qD)
plant_poll_increase2 = plant_poll_increase %>% filter(t == max(t)) %>% pull(qD)
plant_poll_increase3 = (plant_poll_increase2-plant_poll_increase1)/plant_poll_increase1 * 100

@@

#Pollinators-----
poll_output = readRDS("../Data/Working_files/pollinator_sampling_coverage.rds")
pollinators_curves = readRDS("../Data/Working_files/collectors_curves_pollinators.rds")
#Create dataset
d_poll = poll_output$iNextEst$coverage_based
#Check cols
d_poll$col = d_poll$Method

#Now create tibble with same structure
a_poll = tibble(t = pollinators_curves$Study_sampled, 
           Method = as.character(pollinators_curves$iteration), 
           qD = pollinators_curves$Unique_spp_cumulative,
           col = "Randomizations")

#Bind datasets 
d_poll1 = bind_rows(d_poll, a_poll)
d_poll1_point = d_poll1 %>%  filter(Method == "Observed")
d_poll1_lines = d_poll1 %>%  filter(!Method == "Observed")

#Fix levels
d_poll1_lines = d_poll1_lines %>% 
mutate(col = case_when(Method == "Rarefaction" ~ "Interpolated",
                       Method == "Extrapolation" ~ "Extrapolated",
                       T ~ col))
#Order levels
d_poll1_lines$col = factor(d_poll1_lines$col, levels = c("Randomizations", "Interpolated", "Extrapolated"))
#Plot
p1 = ggplot(d_poll1_lines, aes(x = t, y = qD, group = Method, color = col)) +
geom_line(aes(linetype = col),size = 0.65) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_poll1_point, col = "black", size=2) + 
ylab("Pollinator species") +
xlab("Networks") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off")  +
xlim(0,3000)+
ylim(0, 3000) +
ggtitle("(a)") +
theme(plot.margin = margin(r = 12))

#Plants-----
plant_output = readRDS("../Data/Working_files/plant_sampling_coverage.rds")
plant_curves = readRDS("../Data/Working_files/collectors_curves_plants.rds")
#Create dataset
d_plant = plant_output$iNextEst$coverage_based
#Check cols
d_plant$col = d_plant$Method
#Now create tibble with same structure
a_plant = tibble(t = plant_curves$Study_sampled, 
           Method = as.character(plant_curves$iteration), 
           qD = plant_curves$Unique_spp_cumulative,
           col = "Randomizations")

#Bind datasets 
d_plant1 = bind_rows(d_plant, a_plant)
d_plant1_point = d_plant1 %>%  filter(Method == "Observed")
d_plant1_lines = d_plant1 %>%  filter(!Method == "Observed")

#Fix levels
d_plant1_lines = d_plant1_lines %>% 
mutate(col = case_when(Method == "Rarefaction" ~ "Interpolated",
                       Method == "Extrapolation" ~ "Extrapolated",
                       T ~ col))
#Order levels
d_plant1_lines$col = factor(d_plant1_lines$col, levels = c("Randomizations", "Interpolated", "Extrapolated"))

#Plot
p2 = ggplot(d_plant1_lines, aes(x = t, y = qD, group = Method, color = col)) +
geom_line(aes(linetype = col), size = 0.65) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_plant1_point, col = "black", size=2) + 
ylab("Plant species") +
xlab("Networks") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off")  +
xlim(0,3000)+
ylim(0, 3000)+
ggtitle("(b)")+
theme(plot.margin = margin(r = 12))

#Interactions-----
int_output = readRDS("../Data/Working_files/interactions_sampling_coverage.rds")
interactions_curves = readRDS("../Data/Working_files/collectors_curves_interactions.rds")
#Create dataset
d_int = int_output$iNextEst$coverage_based
#Check cols
d_int$col = d_int$Method

#Now create tibble with same structure
a_poll = tibble(t = interactions_curves$Study_sampled, 
           Method = as.character(interactions_curves$iteration), 
           qD = interactions_curves$Unique_spp_cumulative,
           col = "Randomizations")

#Bind datasets 
d_int1 = bind_rows(d_int, a_poll)
d_int1_point = d_int1 %>%  filter(Method == "Observed")
d_int1_lines = d_int1 %>%  filter(!Method == "Observed")

#Fix levels
d_int1_lines = d_int1_lines %>% 
mutate(col = case_when(Method == "Rarefaction" ~ "Interpolated",
                       Method == "Extrapolation" ~ "Extrapolated",
                       T ~ col))
#Order levels
d_int1_lines$col = factor(d_int1_lines$col, levels = c("Randomizations", "Interpolated", "Extrapolated"))
#Plot
p3 = ggplot(d_int1_lines, aes(x = t, y = qD, group = Method, color = col)) +
geom_line(aes(linetype = col), size = 0.65) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_int1_point, col = "black", size=2) + 
ylab("Unique interactions") +
xlab("Networks") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off")  +
xlim(0,3000) +
ylim(0, 30000)+
ggtitle("(c)")

@@

#Create dataset
d_pp = plant_poll_output$iNextEst$coverage_based
#Check cols
d_pp$col = d_pp$Method

#Now create tibble with same structure
a_poll = tibble(t = plant_poll_curves$Plant_sampled, 
           Method = as.character(plant_poll_curves$iteration), 
           qD = plant_poll_curves$Unique_spp_cumulative,
           col = "Randomizations")

#Bind datasets 
d_pp1 = bind_rows(d_pp, a_poll)
d_pp1_point = d_pp1 %>%  filter(Method == "Observed")
d_pp1_lines = d_pp1 %>%  filter(!Method == "Observed")

#Fix levels
d_pp1_lines = d_pp1_lines %>% 
mutate(col = case_when(Method == "Rarefaction" ~ "Interpolated",
                       Method == "Extrapolation" ~ "Extrapolated",
                       T ~ col))
#Order levels
d_pp1_lines$col = factor(d_pp1_lines$col, levels = c("Randomizations", "Interpolated", "Extrapolated"))
#Plot
pp1 = ggplot(d_pp1_lines, aes(x = t, y = qD, group = Method, color = col)) +
geom_line(aes(linetype = col)) +
scale_colour_manual(values = c("gray", "black", "red"), labels = c("Randomizations", "Interpolated", "Extrapolated")) +
scale_linetype_manual(values = c("solid", "solid", "dashed"),  labels = c("Randomizations", "Interpolated", "Extrapolated")) + 
geom_ribbon(aes(ymin = qD.LCL, 
    ymax=qD.UCL, fill = col),alpha=0.2, colour = NA, show.legend = FALSE)+
scale_fill_manual(values = c("gray", "black", "red")) +
geom_point(data = d_pp1_point, col = "black") + 
ylab("Pollinator species") +
xlab("Plant species") +
theme_bw() +
coord_cartesian(expand = FALSE, clip = "off") +
ggtitle("(d)") +
scale_x_continuous(breaks = seq(0, 2800, by = 1000), limits=c(0,2800)) +
scale_y_continuous(breaks = seq(0, 2800, by = 1000), limits=c(0,2600)) +
theme(legend.position = "none")
